When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-03-31 presentation/inbreeding.Rmd
Update slides
More slides

@@

![](images/beta_slopes.png)

Multi-locus genetic architecture:

- Fixed inbreeding depression for individual *f*
- Allele values at 10 loci increase (positive) or decrease (negative) inbreeding
- Allele values sum additively to determine overall inbreeding behaviour phenotype

@@

Multi-locus genetic architecture:

- Fixed inbreeding depression for individual *f*
- Allele values at 10 loci increase (positive) or decrease (negative) inbreeding
- Allele values sum additively to determine overall inbreeding behaviour phenotype

@@

**Selection against being inbred does not necessarily imply selection against inbreeding**

@@

>>>>

<center>
![](images/pop_gen_inds.png)
</center>

@@

<center>
![](images/quant_inds.png)
</center>

<center>

![](images/fixed_ID_inds.png)

</center>

<center>
![](images/neutral_exp_inds.png)
</center>

@@

High variation of inbreeding behaviour across inbreeding depression slopes.

@@

Selection against being inbred does not necessarily imply selection against inbreeding

@@

<center>
![](images/poly_inds.png)

</center>

<center>
![](images/mate_select_1.png)

</center>

<center>
![](images/mate_select_2.png)

</center>

<center>
![](images/mate_select_3.png)

</center>

<center>
![](images/mate_select_4.png)

</center>

<center>
![](images/mate_select_5.png)

</center>

<center>
![](images/mate_select_6.png)

</center>

<center>
![](images/mate_select_7.png)

</center>

<center>
![](images/poly_allele_res.png)

</center>

<center>
![](images/poly_pheno_res.png)

</center>
